\section{Course Projects}
 \begin{itemize}

\item\textsc{Toy C Compiler} [2018]\\
\footnotesize{Implemented a Toy C Compiler using Flex Bison and LLVM as part of the Compiler Course Work. It contains LLVM IR code generation and implementation of some basic optimizations.}\\ 
\phantom{.}\hfill
Code: \href{https://github.com/sandeep007734/Toy-C-Compiler-using-Flex-Bison-LLVM}{https://github.com/sandeep007734/Toy-C-Compiler-using-Flex-Bison-LLVM}


\item \normalsize{\textsc{Distributed Computing.}} [2012]\\
\footnotesize{Wrote \href{https://docs.google.com/viewer?a=v&pid=sites&srcid=ZGVmYXVsdGRvbWFpbnxzYW5kZWVwa3VtYXJ3ZWJzaXRlfGd4Ojc0OGQwYWEwZWYxMDgzMjE}{Distributed Programs} to solve TSP (Travelling sales man problem), ABP (Alpha Beta pruning search) and MST (Minimum spanning tree) using \textit{rpcgen} in C++ and showed a speed up of factor 9, 6 and 2.5 respectively when the number of servers went up from 1 to 6.}\hfill\small Advisor: \href{http://www.researchgate.net/profile/R_Hansdah/publications}{Prof. R.C. \textsc{Hansdah}}\\
\phantom{.}\hfill Report: \href{https://goo.gl/BnTpTF}{https://goo.gl/BnTpTF}

\item \normalsize{\textsc{Communication Network.}} [2012]\\
\footnotesize{Studied the algorithm \href{https://docs.google.com/viewer?a=v&pid=sites&srcid=ZGVmYXVsdGRvbWFpbnxzYW5kZWVwa3VtYXJ3ZWJzaXRlfGd4OjIyMWM1MDYxYjQ2MTVmNw}{SOFA (Sleep optimal Fair attention)}, which aims the energy conservation in wireless devices by changing the scheduling policy by simulating it to see the performance. }\\
\phantom{.}\hfill\small Advisor: \href{http://stochastic.csa.iisc.ernet.in/~shalabh/}{Prof. Shalabh \textsc{Bhatnagar}}\\ \phantom{.}\hfill Report: \href{https://goo.gl/Lh5QQ9}{https://goo.gl/Lh5QQ9}

\item \normalsize{\textsc{Game Theory.}} [2012]\\
\footnotesize{Studied existing scheme for handling \href{https://docs.google.com/viewer?a=v&pid=sites&srcid=ZGVmYXVsdGRvbWFpbnxzYW5kZWVwa3VtYXJ3ZWJzaXRlfGd4OjM4ZDhjYjhkYWJmM2Y0MDU}{Kidney Exchange Programs} and proposed a new scheme \textbf{SPAR} for this.}\\
\phantom{.}\hfill\small Advisor: \href{http://lcm.csa.iisc.ernet.in/hari/}{Prof. Y. \textsc{Narahari}}\\ \phantom{.}\hfill Report: \href{https://goo.gl/3Mujoh}{https://goo.gl/3Mujoh}

%\item \normalsize{\textsc{Network and Distributed Systems Security.}} [2012]\\
%\footnotesize{Design and implemented a Secure Email server, using \textit{Diffie Hellman} key exchange algorithm for secure exchange of keys and \textit{DES} algorithm for encrypting the messages using the keys exchanged earlier. \textit{SHA-512} hashing algorithm was used to store password on server side.}\hfill\small Advisor: \href{http://www.researchgate.net/profile/R_Hansdah/publications}{Prof. R.C. \textsc{Hansdah}}\\

%\item \normalsize{\textsc{Software Architecture.}} [2012]\\
%\footnotesize{Design and Implemented Hospital Insurance Portal using \textit{MVC (Model View Controller)} architecture for managing the insurance related activities of a Hospital and communicate with other services using \textit{REST} architecture. It had two Views, Desktop and Mobile, using the same Model and Controller. The Design was kept the design simple and flexible, so that it should be easy to upgrade.}\hfill\small Advisor: \href{https://www.linkedin.com/pub/raghu-hudli/3/582/ba4}{Prof. Raghu \textsc{Hudli}}\\

 \end{itemize}