%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    { Doctor of Philosophy (DGPA: 9.4/10)} % Degree
    {Indian Institute of Technology Delhi} % Institution
    {New Delhi, India} % Location
    {Jul. 2017 - Jul. 2022 (Expected)} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item Advised by Prof. S. R. Sarangi
\item Thesis: ``Secure Computing''. We study the challenges faced in today's world in the secure execution of an application on an untrusted system. 
      \end{cvitems}
    }


  \cventry
{Master of Engineering in Computer Science ($1^{st}$ class, CGPA: 5.9/8 )} % Degree
{Indian Institute of Science } % Institution
{Bangalore, India} % Location
{Jul. 2011 - Aug. 2013} % Date(s)
{
	\begin{cvitems} % Description(s) bullet points
\item Thesis: ``Modeling Storage Performance in an HPC System''. We analyzed the performance of a parallel file system (GlusterFS, in our case) and study the factors (size of read/write, amount of read/write, replications, striping, network speed, underlying file system. etc.) that impacts its performance in an high performance computing system.
		\item Advised by Prof. K. Gopinath
\item Thesis: \href{https://tinyurl.com/yezfhmdw}{https://tinyurl.com/yezfhmdw}
	\end{cvitems}
}

  \cventry
{Bachelor of Technology in Computer Science ($1^{st}$ class, $73.4\%$)} % Degree
{Ambedkar Institute of Technology (Guru Gobind Singh Indraprastha University) } % Institution
{New Delhi, India} % Location
{Jul. 2007 - Aug. 2011} % Date(s)
{
%	\begin{cvitems} % Description(s) bullet points
%		\item Advised by Prof. K. Gopinath
%	\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
