\newpage
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%\begin{enumerate}[before=\color{black}\sffamily]
%
%%\item \textbf{Intel Labs}, Graduate Research Intern, Bangalore, India, June 2020 - Jan 2021
%%\item \textbf{Indian Institute of Science}, Research Associate. Bangalore, India, 2014 - 2017.
%%\item \textbf{Dell R\&D}, Software Development Engineer. Bangalore, India, 2013 - 2014.
%
%\end{enumerate}
%%---------------------------------------------------------
  \cventry
%{}{}
    { Graduate Research Intern} % Job title
 {  Intel Labs} % Organization
    { Bangalore, Karnataka (Virtual)} % Location
    {Jul. 2020 - Jan 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked on improving the performance of a page table walk in a tiered memory system -- equipped with traditional DRAM and Intel Optane NVMM, by enabling dynamic, transparent migration of the page table from the high-latency NVMM to low-latency DRAM based on the workload characteristics.
      \end{cvitems}
    }


%%---------------------------------------------------------
  \cventry
%{}{}
    { Research Associate} % Job title
 {   Indian Institute of Science} % Organization
    { Bangalore, Karnataka} % Location
    {Jun. 2015 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Worked on the problem of auto-tuning Hadoop systems based on the workload characteristics to improve the overall performance of the systems. We leverages \textit{stochastic} algorithms to quickly converge to an optimal solution. This work as was published in IEEE Cloud, 2017.
\item Worked on the problem of reducing the cost of a ``Human  gait analysis'' using inexpensive IMU sensors. This work was published in IEEE ICSigSys.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {Dell Research \& Development} % Organization
    { Bangalore, India} % Location
    {Jul. 2013 - Jun. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Responsible for BIOS configuration and system management tools: Dell Command Configure (DCC) and Open Manage Client Instrumentation (OMCI). DCC provides a GUI interface that allows BIOS configuration (Windows and Linux). OMCI is a command-line tool that allows remote management application programs to access information about a client computer.}
		\item Complete Re-branding of DCC to the latest ``flat-look'' design.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
