\cvsection{Selected Projects}
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Course project for Compiler design} % Role
    {Toy C Compiler} % Event
    {Prof. Sorav \textsc{Bansal}} % Location
    {2018, IITD} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented a Toy C Compiler using Flex Bison and LLVM as part of the Compiler Course Work. It contains LLVM IR
        	code generation and implementation of some basic optimizations.}
\item Code: \href{https://github.com/sandeep007734/Toy-C-Compiler-using-Flex-Bison-LLVM}{https://github.com/sandeep007734/Toy-C-Compiler-using-Flex-Bison-LLVM} (private repository).
      \end{cvitems}
    }

  \cventry
    {Course project} % Role
    {Distributed Computing} % Event
    {Prof. R. C. \textsc{Hansdah}} % Location
    {2012, IISc} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Wrote Distributed Programs to solve TSP (Travelling sales man problem), ABP (Alpha Beta pruning search) and MST
        	(Minimum spanning tree) using rpcgen in C++ and showed a speed up of factor 9, 6 and 2.5 respectively when the
        	number of servers went up from 1 to 6.}
	\item Report: \href{https://tinyurl.com/2p97ak33}{https://tinyurl.com/2p97ak33}
      \end{cvitems}
    }


 \cventry
    {Course project} % Role
    {Communication Network} % Event
    {Prof. Shalabh \textsc{Bhatnagar}} % Location
    {2012, IISc} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Studied the algorithm {SOFA (Sleep optimal Fair attention)}, which aims the energy conservation in wireless devices by changing the scheduling policy by simulating it to see the performance.}
\item {Report: \href{https://tinyurl.com/2p8jv6su}{https://tinyurl.com/2p8jv6su}}
      \end{cvitems}
    }


 \cventry
    {Course project} % Role
    {Game Theory} % Event
    {Prof. Y. \textsc{Narahari}} % Location
    {2012, IISc} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Studied existing scheme for handling ``Kidney Exchange Programs'' and proposed a new scheme \textbf{SPAR} for this.}
	\item Report: \href{https://goo.gl/3Mujoh}{https://goo.gl/3Mujoh}
      \end{cvitems}
    }


 \cventry
    {Course project} % Role
    {Network and Distributed Systems Security} % Event
    {R.C. Hansdah} % Location
    {2012, IISc} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and implemented a Secure Email server, using \textit{Diffie Hellman} key exchange algorithm for secure exchange of keys and \textit{DES} algorithm for encrypting the messages using the keys exchanged earlier. \textit{SHA-512} hashing algorithm was used to store password on server side.}
      \end{cvitems}
    }


\cventry
    {Course project} % Role
    {Software Architecture} % Event
    {Prof. Raghu \textsc{Hudli}} % Location
    {2012, IISc} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Design and Implemented Hospital Insurance Portal using \textit{MVC (Model View Controller)} architecture for managing the insurance related activities of a Hospital and communicate with other services using \textit{REST} architecture. It had two Views, Desktop and Mobile, using the same Model and Controller. The Design was kept the design simple and flexible, so that it should be easy to upgrade.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
