
\cvsection{Selected Publications}


\begin{cventries}

\begin{enumerate}[before=\color{black}\sffamily]


\item {\it TierScape: Harnessing Multiple Compressed Tiers to Tame Server Memory TCO.}\\
{\bf Sandeep Kumar}, Aravinda Prasad, and Sreenivas Subramoney.\\
In {\bf EuroSys} 2026.


\item {\it TierTrain: Proactive Memory Tiering for CPU-Based DNN Training.}\\
Sathvik Swaminathan, {\bf Sandeep Kumar}, Aravinda Prasad, and Sreenivas Subramoney.\\
In {\bf ISMM}, Seoul, South Korea, 2025.

\item \textit{A Tug-of-War between Static and Dynamic Memory in Intel SGX}.
\\
\textbf{Sandeep Kumar}, Abhisek Panda, Advait Nerlikar and Smruti R. Sarangi.\\
In {\bf VLSID}, Bangalore, India, 2025.


\item \textit{Telescope: Telemetry for Gargantuan Memory Footprint Applications}.
\\
Alan Nair, \textbf{Sandeep Kumar}, Aravinda Prasad, Ying Huang, Andy Rudoff, Sreenivas Subramoney. \\
In \textbf{USENIX ATC}, Santa Clara, USA, 2024.

\item \textit{Taming Server Memory TCO with Multiple Software-Defined Compressed Tiers}.
\\ 
\textbf{Sandeep Kumar}, Aravinda Prasad, Sreenivas Subramoney.
In \textbf{Arxiv}, 2024.

\item \textit{Managing Large Enclaves in a Data Center}.
\\
\textbf{Sandeep Kumar}, Smruti R. Sarangi.
In \textbf{Arxiv}, 2024.

\item \textit{ Perspector: Benchmarking Benchmark Suites 
}.\\\textbf{Sandeep Kumar}, Abhisek Panda, Smruti R. Sarangi. In \textbf{DATE}, Antwerp, Belgium, 2023.

\item \textit{Hardware-Assisted Mechanisms to Enforce Control Flow Integrity: A Comprehensive Survey}.\\\textbf{Sandeep Kumar}, Diksha Moolchandani, Smruti R. Sarangi. In Journal of Systems Architecture (JSA)

\item \textit{SecureLease: Maintaining Execution Control in The Wild using Intel SGX}.\\ \textbf{Sandeep Kumar}, Abhisek Panda, and Smruti R. Sarangi. In \textbf{Middleware}, Quebec City, Canada, 2022.

\item \textit{SGXGauge: A Comprehensive Benchmark Suite for Intel SGX.}
\\ \textbf{Sandeep Kumar}, Abhisek Panda, and Smruti R. Sarangi.. In  \textbf{ISPASS}, Singapore, 2022.

%----------
	\item \textit{SecureFS: A Secure File System for Intel SGX}.\\
\textbf{Sandeep Kumar} and Smruti R. Sarangi. In \textbf{RAID}, Spain, 2021.

	\item \textit{Radiant: Page Table Management for Heterogeneous Memory Systems.}\\
\textbf{Sandeep Kumar}, Aravinda Prasad, Smruti R. Sarangi, and Sreenivas Subramoney. In \textbf{ISMM}, Canada, 2021.

	\item \textit{F-LaaS: A Control-Flow-Attack Immune License-as-a-Service Model}.\\
\textbf{Sandeep Kumar}, Diksha Moolchandani, Takatsugu Ono, and Smruti Sarangi. In \textbf{IEEE SCC}, Milan, Italy, 2019.
	
% 	\item\textit{Towards a Portable Human Gait Analysis \& Monitoring System }. \\
% \textbf{Sandeep Kuma}r, Poorna Talkad Sukumar, K. Gopinath, Dr. Jayanth Sampath, Laura Rocchi, and Suyameendra Kulkarni..In \textbf{IEEE ICSigSys}, Bali, Indonesia, 2018. 
	
	\item \textit{Scalable Performance Tuning of Hadoop MapReduce: A Noisy Gradient Approach}.\\
\textbf{Sandeep Kumar}, Sindhu Padakandla, Chandrashekar L, Priyank Parihar, Gopinath K, and Shalabh Bhatnagar. In \textbf{IEEE Cloud}, Hawaii, USA, 2017. 
\end{enumerate}

% Google Scholar Page: \url{https://scholar.google.co.in/citations?hl=en&user=2Ge6tWwAAAAJ}
% Google scholar page with link https://scholar.google.co.in/citations?hl=en&user=2Ge6tWwAAAAJ


%---------------------------------------------------------
%  \cventry
%    {\textbf{Sandeep Kumar}, Diksha Moolchandani, Takatsugu Ono and Smruti Sarangi.} % Affiliation/role
%    { F-LaaS: A ControlFlow-Attack Immune License-as-a-Service Model} % Organization/group
%    {IEEE SCC} % Location
%    {July 2019} % Date(s)
%    {
%      \begin{cvitems} 
%      \end{cvitems}
%    }


%---------------------------------------------------------
\end{cventries}

\newpage

\cvsection{Patents}


\begin{cventries}

\begin{enumerate}[before=\color{black}\sffamily]


	\item CONTEXT-AWARE MEMORY TIERING FOR MACHINE LEARNING TRAINING (Submitted)
	\newline Sathvik Swaminathan, Sandeep Kumar, Aravinda Prasad, Sreenivas Subramoney

	\item METHODS AND APPARATUS TO PROFILE PAGE TABLES FOR MEMORY MANAGEMENT (Patent Granted)
	\newline Aravinda Prasad, Sandeep Kumar, Sreenivas Subramoney

	

\end{enumerate}


\end{cventries}
