\section{Current Research Projects}
\begin{itemize}

\item 
\normalsize{\textsc{Optimizing performance of applications in NV-MM}}\\
\footnotesize{Modern servers are adopting the large size but high-latency persistent memory of NV-MM to accommodate applications with large memory footprint. However, the performance suffers as the operating system does not take into account the different characteristics of the DRAM and the NV-MM. We are working on improving the performance of such application via the kernel support.}

\item 
\normalsize{\textsc{SecureFS: A Secure File System for Intel SGX}} \\
\footnotesize{In this project, we are exploring an efficient and secure file system support for applications running in a secure enclave provided by Intel SGX, which does not support system calls and consequently, the file system in its current form.}
\begin{flushright}
Advisor: \href{http://www.cse.iitd.ac.in/~srsarangi/}{Prof. Smruti R. \textsc{Sarangi}}
\end{flushright}

%\item 
%\normalsize{\textsc{Survey of Hardware assisted defense methods for CFI.}} \\
%\footnotesize{We are working on a through analysis of hardware assisted defense methods to maintain control flow integrity of a binary's execution.}
%\begin{flushright}
%Advisor: \href{http://www.cse.iitd.ac.in/~srsarangi/}{Prof. Smruti R. \textsc{Sarangi}}
%\end{flushright}

\item 
\normalsize{\textsc{Security aspects of a Remote Operations System or ROS}} \\
\footnotesize{ROS is widely used in autonomous vehicles. In this project, we are exploring the current security challenges for a ROS based system and propose an efficient solution for it.}
\begin{flushright}
Advisor: \href{http://www.cse.iitd.ac.in/~srsarangi/}{Prof. Smruti R. \textsc{Sarangi}}
\end{flushright}

\item 
\normalsize{\textsc{Hardware assisted Control Flow Integrity}} \\
\footnotesize{We are looking at ways to ensure the control flow integrity of a binary. Several attacks are mounted on the execution of a binary, which violates confidentiality or integrity or both. A trusted execution environment, which guarantees a secure execution environment, has severe limitations in its current form. We are exploring ways to alleviate these problems.
}
\begin{flushright}
Advisor: \href{http://www.cse.iitd.ac.in/~srsarangi/}{Prof. Smruti R. \textsc{Sarangi}}
\end{flushright}


%\item \input{tex_files/tejas}

%\item \input{spsa_hadoop}
%\item \input{gait}
 \end{itemize}

%\section{Past Research Projects}
%\begin{itemize}
%\item \input{tex_files/modelling_storage}
% \end{itemize}